---
title: "Course Overview"
output:
   html_document:
    toc: true
    code_folding: null
    number_sections: false
    theme: "cerulean"
---

***

## Webinar Information

Please use the following [Zoom link](https://smithsonian.zoom.us/j/87901849006?pwd=VzdJSFM3Z2hWN2krZGlVbWwvTnFJUT09) and meeting information to log-in to the lecture sessions. The lecture sessions will also be **recorded** and posted online at a later time following the workshop.

**Coral Genetics Workshop / Taller Genética ** [Zoom Link](https://smithsonian.zoom.us/j/87901849006?pwd=VzdJSFM3Z2hWN2krZGlVbWwvTnFJUT09)  
Meeting ID: 879 0184 9006  
Passcode: genetica  
(works for all lecture sessions)  

***

## Course Location

The in-person course will be hosted at the University of Costa Rica [(UCR)](https://www.ucr.ac.cr/) Rodrigo Facio campus in San José, Costa Rica. The hands-on laboratory training sessions will be held in the Centro de Investigación en Ciencias del Mar y Limnología [(CIMAR)](http://cimar.ucr.ac.cr/) molecular laboratories.
```{r include = FALSE}
library(leaflet)
library(dplyr)
```
```{r echo=FALSE}
# Use the leaflet map below to explore the UCR campus area. 
leaflet() %>%
  setView(lng=-84.048011, lat=9.937697, zoom = 16) %>%
  addTiles() %>%
  addMarkers(lng=-84.043839, lat=9.939399, popup="University of Costa Rica CIMAR laboratory") 
```

***

## Course Schedule

```{r schedule_table, echo = FALSE, message = FALSE}
library("tidyverse")
schedule <- read_csv("./csvs/schedule.csv")
knitr::kable(schedule)
```

***

## Course Materials
### Lecture Sessions

Lecture I. **Introduction to the course** - Slide Links: [ES](https://drive.google.com/file/d/1ftIh5SuB7WzQQHMdXtOZbxhqnlBC65pr/view?usp=sharing), [EN](https://drive.google.com/file/d/10rGOLci_T9MWXvaupDgHetk1TH8p1z0H/view?usp=sharing)  

  * Instructors
  * Participants
  * Course Goals  
  

Lecture II. **Costa Rica coral restoration** - Slide Links *will be posted before the course*: [ES](), [EN]()  

  * [Raising Coral Costa Rica](https://www.raisingcoral.org/)
  * [Culebra Reef Gardens](https://culebrareefgardens.org/home/)
  * *Pocillopora* samples to be analyzed during the workshop  
  

Lecture III. **Fundamentals of genetics and evolution** - Slide Links: [ES](https://drive.google.com/file/d/1krFC8hoQ-p89hlLXsp1C42ijPoYbOoFT/view?usp=sharing), [EN](https://drive.google.com/file/d/1P0lsIbODf_r90NwCZx9WraCqbTxeAqwy/view?usp=sharing)  

  * DNA structure and chromosomal organization
  * Mendelian inheritance
  * Evolution by natural selection
  * Molecular methods in genetics
	 - DNA extraction
	 - Polymerase chain reaction
	 - Gel electrophoresis
	 - Restriction fragment length polymorphism  
	 - Sequencing
	 

Lecture IV. **Introduction to conservation genetics and species delimitation** - Slide Links *will be updated*: [ES](https://drive.google.com/file/d/14TfRnt9PG4GEE4P_sIgNit0V8Teu3RZy/view?usp=sharing), [EN](https://drive.google.com/file/d/1LFBl4LjfVHU7ksbZHxAy7JnzaRfzLhUL/view?usp=sharing)  

  * Extinction
  * Genetic diversity 
  * Importance of species delimitation and taxonomy
  * Measuring genetic diversity - mtDNA, microsatellites, SNPs, whole genomes  
  

Lecture V. **Eastern Pacific coral diversity** - Slide Links *will be posted before the course*: [ES](), [EN]()  

  * Families
      + *Carophyllia*
      + *Fungia*
      + *Gardinoseris*
      + *Leptoseris*
      + *Pavona*
      + *Pocillopora*
      + *Porites*
      + *Psammocora*
      + *Tubastrea*


Lecture VI. **Coral-algae symbiosis in the eastern tropical Pacific** - Slide Links *will be posted before the course*: [ES](), [EN]()  


Lecture VII. **Coral biodiversity research at the Smithsonian: STRI field research and NMNH historical collections** - Slide Links: [ES](https://drive.google.com/file/d/1ekine8rnY9zsAmUe0pV6V7HRlRwqVXJ0/view?usp=sharing), [EN]()  

  * Anthozoan evolution, coral diversity and morphology-based taxonomy
  * Coral extinctions and current trajectories


Lecture VIII. **Conservation genetics for coral restoration** - Slide Links *will be updated*: [ES](https://drive.google.com/file/d/1S3cMwoqDxorr0WaT2PJua1HxdYXZUxsp/view?usp=sharing), [EN](https://drive.google.com/file/d/1lKHkJji0eq91EhM9P92-gcCjYI6wQFEX/view?usp=sharing)  


Lecture IX. **Genomics and high-throughput sequencing in conservation biology** - Slide Links *will be updated*: [ES](https://drive.google.com/file/d/1EmuCqtuH8cisr4jkWRg11gjBNAKLUBFW/view?usp=sharing), [EN](https://drive.google.com/file/d/1wXuxkSmgJhqv5lWOu7C5cQe8qj5A6pww/view?usp=sharing)  


### Laboratory Hands-On Sessions

Laboratory safety and techniques

Lab 1. **DNA extraction**  

  * DNA extraction will be performed with the Qiagen DNeasy PowerSoil Pro Kit
  * Protocol Links: [ES](https://drive.google.com/file/d/1c5kTg3llYlYgRiyu2CCPPEdTObcuLxtl/view?usp=sharing), [EN](https://drive.google.com/file/d/11rGMrUuXiuhXqGx6Fd1g0n-R2nI1pBQ-/view?usp=sharing)  


Lab 2. **DNA concentration, purity and quality check**  
  
  * DNA concentration and purity will be assessed using a NanoDrop 2000c spectrophotometer
  * Protocol Links: [ES](https://drive.google.com/file/d/1qO7sQDhuevmObZRFhXduCLyslAoKO3Tb/view?usp=sharing), [EN](https://drive.google.com/file/d/1Hrd1CgEKrNJSENGeZmMJzJaUSG7eB1IW/view?usp=sharing)  
  
  
Lab 3. **Polymerase chain reaction (PCR)**  

  * Barcoding PCR will be performed for the *Pocillopora* mtORF, histone 3, and HSP70 loci
  * Protocol Links: [ES](https://drive.google.com/file/d/1EvOnqZw1gyBvOeh_lQBrsTHxsGO2K6bZ/view?usp=sharing), [EN](https://drive.google.com/file/d/12TYm0kLN3vuJRRhn8vMLkyn68kLIP8h6/view?usp=sharing)  

Lab 4. **Gel electrophoresis**  

  * Gel electrophoresis will be completed to visualize the success of DNA extraction and PCR techniques
  * Protocol Links: [ES](https://drive.google.com/file/d/173HWs-nD_pMv9V7L405Hktx0pSY_TleX/view?usp=sharing), [EN](https://drive.google.com/file/d/1s4ijP--fesd14dn7vj8dzXHbuZrcobwC/view?usp=sharing)  
  
Lab 5. **PCR cleanup and Sanger sequencing preparation**  

  * Protocol Links *will be posted*: [ES](), [EN]()  

Lab 6. **Restriction fragment length polymorphism (RFLP) assays**  

  * Protocol Links *will be posted*: [ES](), [EN]()  

*Note that some protocols may be updated prior to the workshop laboratory sessions*
